### 2018-08-15 introduction.tex
proper citation
amon --> among

\section{Introduction}
% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.
The \gls{MSR} is an advanced nuclear reactor developed at \gls{ORNL} 
in the 1950s and operated in the 1960s. More recently, the \gls{GIF} included 
\glspl{MSR} amon the six advanced reactor concepts promising for further 
research and development.
\glspl{MSR} offer significant improvements ``in the four broad areas of 
sustainability, economics, safety and reliability, and proliferation resistance 
and physical protection" \cite{doe_technology_2002}. To achieve the goals 
formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and 
improve inherent safety by using liquid fuel.

@@

Nuttin \emph{et al.} broke up reactor core geometry into three \gls{MCNP} cells: 
one for salt channels, one for the salt plena above and below the core and the 
last cell for the annulus, consequently, the two-region reactor core was 
approximated by one region with averaged fuel/moderator ratio 
\cite{nuttin_potential_2005}.  A similar approach was used by Powers \emph{et 
al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} 
\cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, 
betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016}. This 
clearly misrepresent the two-region breeder reactor concept. The unit-cell or 
one-region models may produce reliable results for homogeneous reactor cores 
(i.e. \gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs 
(i.e. \gls{MSRE}). However, a two-region \gls{MSBR} must be simulated using a whole-core 
model to capture different neutron transport characteristics in the inner and 
outer regions of the core. In particular, most fissions happens in the inner 
region while breeding occurs in the outer zone.

>>>>

\section{Introduction}
% State the objectives of the work and provide an adequate background, avoiding
% a detailed literature survey or a summary of the results.
The \gls{MSR} is an advanced nuclear reactor developed at \gls{ORNL} 
in the 1950s and operated in the 1960s. More recently, the \gls{GIF} included 
\glspl{MSR} among the six advanced reactor concepts promising for further 
research and development.
\glspl{MSR} offer significant improvements ``in the four broad areas of 
sustainability, economics, safety and reliability, and proliferation resistance 
and physical protection" \cite{doe_technology_2002}. To achieve the goals 
formulated by the GIF, \glspl{MSR} attempt to simplify the reactor core and 
improve inherent safety by using liquid fuel.

@@

Nuttin \emph{et al.} broke up reactor core geometry into three \gls{MCNP} cells: 
one for salt channels, one for the salt plena above and below the core and the 
last cell for the annulus, consequently, the two-region reactor core was 
approximated by one region with averaged fuel/moderator ratio 
\cite{nuttin_potential_2005}.  A similar approach was used by Powers \emph{et 
al.}, Betzler \emph{et al.}, and Jeong \emph{et al.} 
\cite{powers_new_2013,powers_inventory_2014,betzler_modeling_2016, 
betzler_molten_2017, jeong_development_2014, jeong_equilibrium_2016}. This 
approach misrepresents the two-region breeder reactor concept. The unit-cell or 
one-region models may produce reliable results for homogeneous reactor cores 
(i.e. \gls{MSFR}, \gls{MOSART}) or for one-region single-fluid reactor designs 
(i.e. \gls{MSRE}). However, a two-region \gls{MSBR} must be simulated using a whole-core 
model to capture different neutron transport characteristics in the inner and 
outer regions of the core. In particular, most fissions happens in the inner 
region while breeding occurs in the outer zone.
